\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A guide for Vietnamese and International Students

### 2023-06-16 phd-cs-us.tex
Updates from Overleaf

\begin{commentbox}[Vu] 
We usually decide that a full-time PhD candidate is either (i) admit with funding (TA or RA) or (ii) rejected. In other words, in most cases, we either
admit you with full funding, or we don't. In some rare cases, we admit
without funding because you have funding on your own (e.g.,
supported by your government or having external grants). We also justify
our decision with a summary about your application, where we list
strengths (e.g., well-known school) and weaknesses (e.g., weak
LORs). 
\end{commentbox}

@@

Tab.~\ref{tab:cost} shows the budget breakdown for a GRA per year (this level of details is what faculty actually uses when applying for funding).
These numbers are based on my experience at public universities in the US.  Private universities may have different numbers.  For simplicity, I will assume the department has a 9-month stipend of \$27000 (GMU actually pays more) and therefore a 3-month summer of \$9000. I will also use GMU tuition rate of about \$15,000/year for full-time study (which is quite cheap compared to private universities, e.g., MIT charges around \$50K) and a 58.9\% rate on \emph{indirect cost}, which is what GMU charges for overhead or administrative costs (yes, after all, universities are businesses!).  Finally, I assume the student makes two conference trips per year, one domestic and one international (so conf. registration, airline tickets, taxi, meals, etc are all included). At the end, the total budget comes out to be \$69K. \emph{The summary is that while you're paid X, your advisor probably pays 2X for you}.

>>>>

\begin{commentbox}[Vu] 
We usually decide that a PhD candidate is either (i) admit with funding (TA or RA) or (ii) rejected. In other words, in most cases, we either
admit you with full funding, or we don't. In some rare cases, we admit
without funding because you have funding on your own (e.g.,
supported by your government or having external grants). We also justify
our decision with a summary about your application, where we list
strengths (e.g., well-known school) and weaknesses (e.g., weak
LORs). 
\end{commentbox}

@@

Tab.~\ref{tab:cost} shows the budget breakdown for a GRA per year (this level of details is what faculty actually uses when applying for funding).
These numbers are based on my experience at public universities in the US.  Private universities may have different numbers.  For simplicity, I will assume the department has a 9-month stipend of \$27000 (GMU actually pays more) and therefore a 3-month summer of \$9000. I will also use GMU tuition rate of about \$15,000/year for full-time study (which is quite cheap compared to private universities, e.g., MIT charges around \$50K) and a 58.9\% (overhead) rate on \emph{indirect cost}, which is what GMU charges for administrative costs (yes, after all, universities are businesses!).  Finally, I assume the student makes conference trips per year, one domestic and one international (so conf. registration, airline tickets, taxi, meals, etc are all included). At the end, the total budget comes out to be \$69K.  \emph{The summary is that while you're paid X, your advisor probably pays 2X for you}.
